A python toolbox to tackle the curse of imbalanced datasets in machine learning

### 2016-06-26 main.tex

% Short headings should be running head and authors last names
\ShortHeadings{A python toolbox to tackle the curse of imbalanced datasets in machine learning}{Lema\^itre, Nogueira, Victor, and Aridas}
\firstpageno{1}

@@

\begin{abstract}
\texttt{UnbalancedDataset} is an open-source python toolbox aiming at providing a wide range of methods to cope with the problem of imbalanced dataset frequently encountered in machine learning and pattern recognition.
The implemented state-of-the-art methods can be categorized into 4 groups: (i) under-sampling, (ii) over-sampling, (iii) combination of over- and under-sampling, and (iv) ensemble learning methods.
The proposed toolbox only depends on \texttt{numpy}, \texttt{scipy}, and \texttt{scikit-learn} and is distributed under MIT license.
Documentation, unit tests as well as integration tests are provided to ease usage and contribution.
The toolbox is publicly available in GitHub \url{https://github.com/fmfn/UnbalancedDataset}.
\end{abstract}

@@

The implementation relies on \texttt{numpy}, \texttt{scipy}, and \texttt{scikit-learn}.
Each class implements 3 main methods inspired from the \texttt{scikit-learn} API:
(i) \texttt{fit} computes the parameter values which are later needed to resample the data into a balanced set;
(ii) \texttt{sample} performs the sampling and returns the data with the desired balancing ratio;
and (iii) \texttt{fit\_sample} is equivalent to calling the method \texttt{fit} followed by the method \texttt{sample}.

@@

The \texttt{UnbalancedDataset} toolbox provides four different strategies to tackle the problem of imbalanced dataset:
(i) under-sampling, (ii) over-sampling, (iii) a combination of both, and (iv) ensemble learning.
The following subsections give an overview of the techniques implemented.

>>>>

% Short headings should be running head and authors last names
\ShortHeadings{A python toolbox to tackle the curse of imbalanced datasets in machine learning}{Lema\^itre, Nogueira, Oliveira, and Aridas}
\firstpageno{1}

@@

\begin{abstract}
\texttt{imbalanced-learn} is an open-source python toolbox aiming at providing a wide range of methods to cope with the problem of imbalanced dataset frequently encountered in machine learning and pattern recognition.
The implemented state-of-the-art methods can be categorized into 4 groups: (i) under-sampling, (ii) over-sampling, (iii) combination of over- and under-sampling, and (iv) ensemble learning methods.
The proposed toolbox only depends on \texttt{numpy}, \texttt{scipy}, and \texttt{scikit-learn} and is distributed under MIT license.
Furthermore, it is fully compatible with \texttt{scikit-learn} and is part of the \texttt{scikit-learn-contrib} supported project.
Documentation, unit tests as well as integration tests are provided to ease usage and contribution.
The toolbox is publicly available in GitHub \url{https://github.com/fmfn/UnbalancedDataset}.
\end{abstract}

@@

The implementation relies on \texttt{numpy}, \texttt{scipy}, and \texttt{scikit-learn}.
Each class implements 3 main methods inspired from the \texttt{scikit-learn} API:
(i) \texttt{fit} computes the parameter values which are later needed to resample the data into a balanced set;
(ii) \texttt{sample} performs the sampling and returns the data with the desired balancing ratio;
and (iii) \texttt{fit\_sample} is equivalent to calling the method \texttt{fit} followed by the method \texttt{sample}.
A class \texttt{Pipeline} is inherited from \texttt{scikit-learn} toolbox to automatically combine \texttt{sampler}, \texttt{transformers}, and \texttt{estimators}.

@@

The \texttt{imbalanced-learn} toolbox provides four different strategies to tackle the problem of imbalanced dataset:
(i) under-sampling, (ii) over-sampling, (iii) a combination of both, and (iv) ensemble learning.
The following subsections give an overview of the techniques implemented.
